Timely Object Recognition

### 2012-06-01 writeups/nips12/technical.tex
oops littel fix
changes and squeezing … also squeeze images
fixed figure1 and little mistake in technical

% \begin{table}[h!]
% \centering
% \caption{Summary of the notation.}
% \label{tab:notation}
% \begin{tabular}{|l|l|}
%   \hline
%   $\mathcal{I}$ & image \\
%   $C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
%   $t$           & time into episode \\ 
%   $T_s$, $T_d$  & start and deadline times \\ 
%   $s^j$         & belief state at step $j$ \\ 
%   $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
%   $\mathcal{A}$ & set of actions $a$\\ 
%   \comment{$\mathcal{F}$ & set of featurization actions \\}
%   \comment{$\mathcal{L}$ & set of classification actions\\}
%   $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{A}$\\
%   $\mathcal{O}$ & set of executed actions\\
%   $\mathbf{o}$  & set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
%   $c(a_i)$        & cost of executing $a_i$, in units of $t$\\
%   \hline
% \end{tabular}\end{table}

@@

We include the following quantities as features $\phi(s,a)$:
\begin{description}
\item[$P(C_a)$] The prior probability of the class that corresponds to the detector of action $a$
\item[$P(C_0|\mathbf{o}) \ldots P(C_1|\mathbf{o})$] The probabilities of all classes, conditioned on the current set of observations.
\item[$H(C_0|\mathbf{o}) \ldots H(C_1|\mathbf{o})$] The entropies of all classes, conditioned on the current set of observations.
\end{description}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
\caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
\label{fig:weights}
\end{figure}

% \subsection{Updating with observations} \label{sec:updating}
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.56\linewidth]{../figures/mrf_w_gist.pdf}
% \caption{
% \todo{get rid of this figure?}
% The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
% }
% \label{fig:model}
% \end{figure}

The bulk of our feature representation is formed by probability of individual class occurrence, conditioned on the observations so far: $P(C_0|\mathbf{o}) \ldots P(C_1|\mathbf{o})$.
This allows the action-value function to learn correlations between presence of different classes, and so the policy can look for the most probable classes given the observations.

>>>>

@@

We include the following quantities as features $\phi(s,a)$:
\begin{description}
\item[$P(C_a)$] The prior probability of the class that corresponds to the detector of action $a$
\item[$P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$] The probabilities of all classes, conditioned on the current set of observations.
\item[$H(C_0|\mathbf{o}) \ldots H(C_K|\mathbf{o})$] The entropies of all classes, conditioned on the current set of observations.
\end{description}

@@

\begin{figure}[h!]
\centering
\subfigure[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
\subfigure[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
% \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
\caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
\label{fig:weights}
\end{figure}

\subsection{Updating with observations} \label{sec:updating}
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.56\linewidth]{../figures/mrf_w_gist.pdf}
% \caption{
% \todo{get rid of this figure?}
% The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
% }
% \label{fig:model}
% \end{figure}

The bulk of our feature representation is formed by probability of individual class occurrence, conditioned on the observations so far: $P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$.
This allows the action-value function to learn correlations between presence of different classes, and so the policy can look for the most probable classes given the observations.
